Macro Impacts

### 2016-08-24 Macro Impacts Revised.tex
further conceptual points added

This suggests that much of the melting occurs once the temperature field is expanding slower than the speed of sound, and that the expansion speed of the melt zone slows down very quickly.

>>>>

This either suggests that much of the melting occurs once the temperature field is expanding slower than the speed of sound, and that the expansion speed of the melt zone slows down very quickly or that the material parameters -- especially $\alpha$ -- are far from constant (or may not even be well defined) in our case.
